NIRCam Faint and Bright Flux Calibration Plan

### 2017-05-08 ms.tex
I added more details to the by eye classification.

>>>>

\subsection{Visual Classification}

As recommended by C. Corbally, the \texttt{mkclass} classifications of near-solar stars were checked by eye.
A graphical user interface explorer was made to compare template classification spectra with the observed Hectospec spectra\footnote{https://github.com/eas342/mkclassfication\_viewer}.
Figure \ref{fig:0738284p2133class} shows the Hectospec spectrum of a source at 07:38:28.4 +21:33 that \texttt{mkclass} identifies as G2~V.
The line ratios of Ca I 4226~$\AA$, H$\delta$, H$\gamma$ and Fe I lines are most consistent with a G2 V type.

\begin{figure}[!hbtp]
\centering
\includegraphics[width=.95\columnwidth]{O_0738284_p2133_class_g2v.pdf}
\caption{An example G2~V source found by \texttt{mkclass} (07:38:28.4 +21:33) is visually checked against spectral templates.
Of particular importance for temperature classification are the Ca I 4226~$\AA$, H$\delta$, H$\gamma$ and Fe I lines highlighted above \citep{gray2009specClass}.
Two standards (G2 V and G1.5 V) are shown for comparison.}\label{fig:0738284p2133class}
\end{figure}
